---
title: "Controlling Animations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Controlling Animations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Methods

'Lottie' offers several methods for controlling various aspects of animations, and 'shinyLottie' provides options for calling these methods when initialising the animation or updating them at a later point. The table below documents the most common methods:

| Method                 | `lottie_animation()` argument | 'shinyLottie' Function                                                      |
|-----------------|-----------------|---------------------------------------|
| Loop                   | `loop`                        | `lottie_setLoop()`                                                          |
| Autoplay               | `autoplay`                    | `lottie_play()`, `lottie_pause()`, and `lottie_stop()`                      |
| Speed                  | `speed`                       | `lottie_setSpeed()`                                                         |
| Direction              | `direction`                   | `lottie_setDirection()`                                                     |
| Play Segments          | `playSegments`                | `lottie_playSegments()`, `lottie_goToAndStop()`, and `lottie_goToAndPlay()` |
| Set Subframe Rendering | `setSubFrame`                 | `lottie_setSubFrame()`                                                      |
| Destroy                | N/A                           | `lottie_destroy()`                                                          |

To demonstrate this, the example below initialises an animation using `lottie_animation()` with a `speed` value of 2, causing the animation to play twice as fast as normal. We can then use a reactive event, triggered by clicking the button, to update the speed to a value of 0.5 (causing it to play twice as slow as normal) using `lottie_setSpeed()`.

```{r eval = FALSE}
library(shiny)
library(shinyLottie)

ui <- fluidPage(
  include_lottie(),
  lottie_animation(
    path = "shinyLottie/example.json",
    name = "my_animation",
    speed = 2
  ),
  actionButton("updateSpeed", "Set Speed to 0.5")
)

server <- function(input, output, session) {
  observeEvent(input$updateSpeed, {
    lottie_setSpeed(speed = 0.5, name = "my_animation")
  })
}

shinyApp(ui, server)
```

Note that when calling `lottie_setSpeed()`, we reference the name of the animation we wish to target (in this case, `"my_animation"`). This is consistent across virtually all 'shinyLottie' functions, allowing for fine control over the animations in your 'shiny' app (i.e. being able to update the speed of a single animation, rather than all animations). Alternatively, the default default `name` value of `"all"` can be used to target all animations in the app.

Finally, if you want to call a 'Lottie' method for which 'shinyLottie' does not provide a function for, this can be achieved using `lottie_callMethod()`.

## Properties

'Lottie' animations have a number of properties that can be queried during runtime. The example below demonstrates how to query the 'playCount' property of an animation using `lottie_getProperty()`.

```{r eval = FALSE}
library(shiny)
library(shinyLottie)

ui <- fluidPage(
  include_lottie(),
  lottie_animation(
    path = "shinyLottie/example.json",
    name = "my_animation"
  ),
  actionButton("getProperty", "Update Play Count"),
  textOutput("playCountOutput")
)

server <- function(input, output, session) {
  observeEvent(input$getProperty, {
    lottie_getProperty(name = "my_animation", property = "playCount")
  })

  observe({
    req(input$playCount)
    output$playCountOutput <- renderText({
      paste("Play Count:", input$playCount)
    })
  })
}

 shinyApp(ui, server)
```
